\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Bias}
\author{Jonas Gonçalves}
\date{January 2020}

\begin{document}

\maketitle

\section{Introduction}

    Artificial Intelligence is becoming increasingly present in everyday life, on our homes, work, roads and so many other places. As the use of AI increases, is essential to build trust in the system that we are utilizing.
    
    But, transparency is not everything that is desired. Is important to ensure that AI decision-making is unbiased.

\section{Definition}

    Bias is the disproportionate weight in favor or against an idea or thing, usually in a way that is closed-minded, prejudicial, or unfair. Biases can be innate or learned.
    
    A statistical bias results from an unfair sampling of a population, or from an estimation process that doesn't give accurate results on average.
    
\section{Machine Learning}
    
    Bias is a source of error in your model that causes it to over-generalize and underfit your data. If average predicted values are far from the actual values then the bias is high,  and it could cause an algorithm to miss relevant relationships between input and output variables. 
    
    Variance is not the same as bias, it represents the sensitivity to noise in the data that causes your model to overfit.
    
    Inductive bias occurs within the field of machine learning, on this field the objective is to develop algorithms that are able to learn from the training data and anticipate particular outputs in the future.
    
    The inductive bias of the algorithm is the set of assumptions that it uses to predict outputs given that inputs that it hasn't encountered. This can lead the learner towards the correct solution, incorrect, or correct some of the time.
    
    Occam's Razor, which assumes that the simplest consistent hypothesis is the best is a classical example of an inductive bias.
    
\section{Bibliography}
    
    \begin{itemize}
        \item[1.] https://en.wikipedia.org/wiki/Bias 
        \item[2.] https://en.wikipedia.org/wiki/Machine\_learning\#Bias
        \item[3.] https://www.techrepublic.com/article/bias-in-machine-learning-and-how-to-stop-it/
        \item[4.] https://medium.com/datadriveninvestor/bias-and-variance-in-machine-learning-51fdd38d1f86
        \item[5.] https://www.quora.com/What-is-bias-in-machine-learning-algorithms

    \end{itemize}
    
\end{document}
